Shift-sensitive Power Transformations for Transforming Data to Normality

### 2023-04-06 manuscript/manuscript.Rmd
Empirical goodness of fit test is now derived from distributions with fewer instances.

usethis::use_data(
  gof_lookup_table, 
  two_sided_function_parameters, 
  internal = TRUE, 
  overwrite = TRUE)
```
```{r include = FALSE, eval = FALSE}
# This generates the data for the table below.
table_data <- .get_test_statistics_data(manuscript_dir = manuscript_dir)
```

@@

\midrule
0.029 & 0.039 & 0.047 & 0.054 & 0.062 & 0.069 & 0.090 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}
```

>>>>

usethis::use_data(
  gof_lookup_table, 
  two_sided_function_parameters, 
  internal = TRUE, 
  overwrite = TRUE)
```

```{r include = FALSE, eval = FALSE}
# This generates the data for the table below.
table_data <- .get_test_statistics_data(manuscript_dir = manuscript_dir)
```

@@

\midrule
0.042 & 0.063 & 0.077 & 0.090 & 0.106 & 0.118 & 0.159 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}
```
